---
title: "Simple Linear Regression"
author: "Jose_A"
date: "17/3/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Regression Week 1: Simple Linear 
Regression Assignment
Predicting House Prices (One Feature)
In this notebook we will use data on house sales in King County, where Seattle is located, to 
predict house prices using simple (One Feature) linear regression. We will:
>
* Compute summary statistics
-- Write function to compute Simple Linear Regression weights using the closed form 
solution
-- Write functions to make predictions of the output given input features
-- Turn the regression around to predict the input/feature given the output
• Compare two different models for predicting house prices

##### 1. Load data

```{r cars}
train_data = read.csv("Data/kc_house_train_data.csv", header=T, sep=",")
test_data = read.csv("Data/kc_house_test_data.csv", header=T, sep=",")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
