---
title: "Simple Linear Regression"
author: "Jose_A"
date: "17/3/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Regression Week 1: Simple Linear 
Regression Assignment
Predicting House Prices (One Feature)
In this notebook we will use data on house sales in King County, where Seattle is located, to predict house prices using simple (One Feature) linear regression. We will:

  * Compute summary statistics
  * Write function to compute Simple Linear Regression weights using the closed form solution
  * Write functions to make predictions of the output given input features
  * Turn the regression around to predict the input/feature given the output
  * Compare two different models for predicting house prices



##### 1. Load data

```{r traindata}
trainData = read.csv("Data/kc_house_train_data.csv", header=T, sep=",")
testData = read.csv("Data/kc_house_test_data.csv", header=T, sep=",")
```

##### 2. Write a generic function that accepts a column of data (e.g a vector) 'input_feature' and another column 'output' and returns the Simple Linear Regression parameters 'intercept' and 'slope'. Use the closed form solution from lecture to calculate the slope and intercept.

```{r SLR function}
SLR_Intercept_Slope <- function(feature, output) {
        inputMean <- mean(feature)
        outputMean <- mean(output)
        
        covar <- sum((feature - inputMean)*(output - outputMean)) / nrow(trainData)
        varia <- sum((feature - inputMean)**2) / nrow(trainData)
        slope <- covar / varia
        intercept <- outputMean - slope*inputMean
        
        return(list(slope = slope, intercept = intercept))
}
```

##### 3. Use the function to calculate the estimated slope and intercept on the training data to predict price given sqft_living

```{r rdo sqft}
sqft <- SLR_Intercept_Slope(trainData$sqft_living, trainData$price)
sqft
```

##### 4. Write a function that accepts a column of data input_features the slope and the intercept you learned, and returns a column of predictions 'predicted_output' for each entry in the input column.

```{r get predictions}
get_predictions <- function(feature, intercept, slope) {
        return(intercept + slope*feature)
}
```

##### 5. QUIZ QUESTION: Using the slope and intercept from (4), what is the predicted price for a house with 2,650 sqft.

```{r predicted price}
predictedPrice <- get_predictions(2650, sqft$intercept, sqft$slope)
predictedPrice
```

##### 6. Write a function that accepts a column of data: input_features and output and the regression parameters slope and intercept and returns the Residual Sum of Squares (RSS).

```{r RSS function}
getRSS <- function(feature, output, intercept, slope) {
        calculatedRSS <- sum((output - (intercept + slope*feature))**2)
        return(calculatedRSS)
}
```

##### 7. QUIZ QUESTION: According to this function and the slope and intercept from (4) what is the RSS for the simple linear regression using sqft to predict prices on the TRAINING data?

```{r get RSS}
rss_sqft_living <- getRSS(trainData$sqft_living, trainData$price, sqft$intercept, sqft$slope)
rss_sqft_living
```

##### 8. Write a function that accepts a column of data output and the regression parameters slope and intercept and outputs the colum of data estimated_input.

```{r get estimatedInputs}
get_estimated_Inputs <- function(output, intercept, slope) {
        estimatedInputs <- (output - intercept)/slope
        return(estimatedInputs)
}
```

##### 9. QUIZ QUESTION: According to this function and the regression slope and intercept from (3) what is the estimated sqft for a house costing $800,000?

```{r get estimatedInput by 800000}
estInputs <- get_estimated_Inputs(800000, sqft$intercept, sqft$slope)
estInputs
```

##### 10. Use the function from (3) to calculate the Simple Linear Regression parameters slope and intercept for estimating price based on number of bedrooms. Save this slope and intercept for later.

```{r SLR number of bedrooms}
numberOfBedrooms <- SLR_Intercept_Slope(trainData$bedrooms, trainData$price)
numberOfBedrooms
```

##### 11. Compute RSS from both models using TEST data

```{r RSS using Test data}
rss_sqft_living <- getRSS(testData$sqft_living, testData$price, sqft$intercept, sqft$slope)
rss_bedrooms <- getRSS(testData$bedrooms, testData$price, numberOfBedrooms$intercept, numberOfBedrooms$slope)
c(rss_sqft_living, rss_bedrooms)
```

##### 12. Compare the RSS from both models, which model has the smallest residual sum of squares? Why do you think this is the case?

The model that uses house size (square feet) has the smallest RSS. This is likely do to the fact that square footage is more predictive of housing price than the number of bedrooms.

