---
title: "Simple Linear Regression"
author: "Jose_A"
date: "17/3/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Regression Week 1: Simple Linear 
Regression Assignment
Predicting House Prices (One Feature)
In this notebook we will use data on house sales in King County, where Seattle is located, to predict house prices using simple (One Feature) linear regression. We will:

  * Compute summary statistics
  * Write function to compute Simple Linear Regression weights using the closed form solution
  * Write functions to make predictions of the output given input features
  * Turn the regression around to predict the input/feature given the output
  * Compare two different models for predicting house prices



##### 1. Load data

```{r traindata}
trainData = read.csv("Data/kc_house_train_data.csv", header=T, sep=",")
testData = read.csv("Data/kc_house_test_data.csv", header=T, sep=",")
```

##### 2. Write a generic function that accepts a column of data (e.g a vector) 'input_feature' and another column 'output' and returns the Simple Linear Regression parameters 'intercept' and 'slope'. Use the closed form solution from lecture to calculate the slope and intercept.

```{r SLR function}
SLR_Intercept_Slope <- function(feature, output) {
        inputMean <- mean(feature)
        outputMean <- mean(output)
        
        covar <- sum((feature - inputMean)*(output - outputMean)) / nrow(trainData)
        varia <- sum((feature - inputMean)**2) / nrow(trainData)
        slope <- covar / varia
        intercept <- outputMean - slope*inputMean
        
        return(list(slope = slope, intercept = intercept))
}
```