---
title: "Multiple Linear Regression"
author: "Jose_A"
date: "18/3/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Regression Week 2: Multiple Linear 

Estimating Multiple Regression Coefficients (Gradient Descent)

In this first notebook we explored multiple regression using lm. Now we will implement our own functions to estimate model parameters using gradient descent.

In this notebook we will cover estimating multiple linear regression weights via gradient descent. We will:

* Add a constant column of 1s to the feature data
* Converte these features from a data frame to a matrix
* Write a predict_output() function
* Write a function to compute the derivative of the regression weights with respect to a single feature
* Write gradient descent function to compute the regression weights given an initial weigth vector, step size and tolerance
* Use the gradient descent function to estimate regression weights for multiple features

##### 1. Load train and test data

```{r dataSets}
trainData = read.csv("../Week-1/Data/kc_house_train_data.csv", header=T, sep=",")
testData = read.csv("../Week-1/Data/kc_house_test_data.csv", header=T, sep=",")
```


##### 2. Write a function that take a data set, a list of features to be used as inputs, and a name of the output (e.g. price). This function should return a features_matrix consisting of first a column of ones followed by columns containing the values of the input features in the data set in the same order as the input list, it should also return an output_array which is an array of the values of the output i the data set (e.g. price)


```{r function Matrix}
get_matrices_list <- function(dataset, features, output) {
        dataset$ones <- 1
        features_matrix <- as.matrix(dataset[, c('ones', features)])
        output_matrix <- as.matrix(dataset[, output])
        return(list(features_matrix = features_matrix, output_matrix = output_matrix))
        
}
```


##### 3. If the features matrix (including the column of 1s for the constant) is stored as a 2D array (matrix) and the regression weights are stored as a 1D array, then the predicted output is just the dot product between the features matrix and the weights. Write a function predict_output() which accepts a 2D array feature_matrix and a 1D array weights and returns a 1D array predictions


```{r function predict_output()}
predict_output <- function(features_matrix, weights) {
        return(features_matrix %*% weights)
}
```


##### 4. If we have the values of a single input feature in an array feature and the prediction errors (predictions - output) then the derivative of the regression cost function with respect to the weight of feature is just wice the dot product between feature and errors. Write a fuction that accepts a feature array and the error array and return sthe derivative (a single number).

```{r function derivative}
feature_derivative <- function(feature_array, errors_array) {
        return(t(feature_array) %*% errors_array)
}
```


##### 5. Now we will use predict_output() and feature_derivative() to write a gradient descent function. Although we can compute the derivative for all the features simultaneously (the gradient) we will explicitly loop over the features individually for simplicity. Write a gradient descent function that does the following:

 * Accepts a feature_matrix, a 1D output array, an array of initial weights, step_size, and a convergence tolerence.
 * While not converged updates each feature weight by subtracting the step size times the derivative for that feature given the current weights
 * At each step computes the magnitude/length of the gradient (square root of the sum of squared components)
 * When the magnitude of the gradient is smaller than the input tolerance, return the final weight vector

Note: instead of using the function feature_derivative() to compute the gradient for each 
feature I used the formula:

                ▽RSS=−2HT(y−Hw)


```{r function gradient descent}
get_gradient_descent <- function(features_matrix, output_array, initial_weights, step_size, tolerance) {
        converged = FALSE 
        weights = initial_weights
        while(!converged){
                predictions = predict_output(features_matrix, weights)
                error = predictions - output_array
                gradient = -2*t(features_matrix) %*% error
                gradient_magnitude = sqrt(sum(gradient**2))
                weights = weights + step_size * gradient
                if(gradient_magnitude < tolerance){
                        converged = TRUE
                }
        }
        return(weights) 
}
```

##### 6. No we will run the regression_gradient_descent function on some acutal data. In particular we will use the gradient descent to estimate the model from Week 1 using just an intercept and slope. Use the following parameters:

 * Features: sqft_living
 * Output: price
 * initial_weights = [1,-47000]
 * step_size = 7e-12
 * tolerance = 2.5e7
 
 
```{r use of Gradient Descent}
initial_weights <- c(-47000, 1)
step_size <- 7e-12
tolerance <- 2.5e7
listMatrices_trainData <- get_matrices_list(trainData, 'sqft_living', 'price')
simple_weights_trainData <- get_gradient_descent(listMatrices_trainData$features_matrix, 
                                listMatrices_trainData$output_matrix, initial_weights, step_size, tolerance)
simple_weights_trainData
```


##### 7. QUIZ QUESTION: What is the value of the weight for sqft_living the second element of simple_weights (rounded to 1 decimal place)


```{r simple_weights}
simple_weights_trainData['sqft_living',]
```


##### 8. Now build a corresponding test_simple_feature_matrix() and test_output() function using test_data. Using test_simple_feature_matrix() and simple_weights compute the predicted house prices on all the test data.


```{r test Data}
listMatrices_testData <- get_matrices_list(testData, 'sqft_living', 'price')
simple_weights_testData <- get_gradient_descent(listMatrices_testData$features_matrix, 
                                listMatrices_testData$output_matrix, initial_weights, step_size, tolerance)
simple_weights_testData
```


##### 9. QUIZ QUESTION: What is the predicted price for the 1st house in the TEST data set for model 1 (rounded to the nearest dollar)


```{r first house price}
test_predictions <- predict_output(listMatrices_testData$features_matrix, simple_weights_testData)
test_predictions[1,]
```

##### 10. Now compute the RSS on all test data for this model. Record the value and store it for later.


```{r RSS test Data}
rss_testData <- sum((testData$price - test_predictions)**2)
rss_testData
```


##### 11. Now we will use the gradient descent to fit a model with more than 1 predictor variable (and an intercept). Use the following parameters:

 * features = ['sqft_living', 'sqft_living15']
 * output = 'price'
 * initial_weights = [-100000, 1, 1,] (intecept, sqft_living, sqft_living_15)
 * step_size = 4e-12
 * tolerance=1e9
 
 